---
title: "Análisis Exploratorio de Datos del Poder Judicial (Femicidios y Violencia Doméstica)"
author: "Katherine Fernández Quiros"
date: "8/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
 base1=read_csv("C:/Users/kathf/Desktop/dataton/PJCROD_VIOLENCIADOMESTICA_V1.csv")
#View(base1)
```


```{r}
library(readr)
 base2=read_csv("C:/Users/kathf/Desktop/dataton/PJCROD_FEMICIDIOS_V1.csv")
View(base2)
```

```{r}
colnames(base2)=c("Periodo","tipo","Femicidio","Cantidad")
attach(base2)

```

```{r}
colnames(base1)=c("Periodo","tipo","Femicidio","Cantidad",)
attach(base1)

```


```{r}
library(readr)
base11 <- read_csv("PJCROD_POLICIALES_V1-2015.csv")
#View(base11)
attach(base11)

```

```{r}
base2015=subset(base11,`GANZUA/VARILLA`=="FEMICIDIO")
```
```


```{r} 
library(readr)
basepol <- read_csv("C:/Users/kathf/Downloads/PJCROD_POLICIALES_V1-2016.csv.crdownload")
#View(basepol)
attach(basepol)
```

```{r}
base2016=subset(basepol,HURTO=="FEMICIDIO")
#2016 no posee femicidios 



```

```{r}
library(readr)
base <- read_csv("PJCROD_POLICIALES_V1-2017.csv")
#View(base)
```

```{r}
base2017=subset(base,`POR DESCUIDO`=="FEMICIDIO")


```

```{r}
library(readr)
base2018pol <- read_csv("C:/Users/kathf/Downloads/PJCROD_POLICIALES_V1-2018.csv")
#View(base2018pol)
attach(base2018pol)

```

```{r}
base2018=subset(base2018pol,BOQUETE=="FEMICIDIO")

```

```{r}
bases=rbind(base2015,base2017,base2018)
femicidios=save(bases,file="femicidios.Rdata")


```



